---
title: "Machine learning for multiple linear regression"
output: 
  html_document: 
    highlight: espresso
    theme: cerulean
---
***

####[Multiple linear regression](https://en.wikipedia.org/wiki/General_linear_model) is a generalization of linear regression by considering more than one independent variable, and a specific case of general linear models formed by restricting the number of dependent variables to one.


### Split data into training and testing chunks
```{r comment=NA,echo=FALSE,message=FALSE}
require(caret)
require(ggplot2)
require(gridExtra)
social <- read.csv("~/GitHub/Machine_Learning/social.csv")
set.seed(1)
inTrain <- createDataPartition(y = social$BounceRate, p = 0.7, list = FALSE)
training <- social[inTrain,] ; testing <- social[-inTrain,]
dim(training) ; dim(testing)



```


###feature plot
```{r, echo=FALSE, fig.height=5, fig.width=6}
featurePlot(x = training[,c("Visits","NewVisits","PageViews")] , y = training$BounceRate,
            plot = "pairs")

```


###Fit a linear model
```{r comment=NA, echo=FALSE}
modFit <- train(BounceRate ~ Visits + NewVisits + PageViews, method = "lm", data = training)

finMod <- modFit$finalModel
 
print(modFit)
```


###Plot fitted versus residuals color by bounce rate
```{r, echo=FALSE, fig.height=5, fig.width=6}
qplot(finMod$fitted.values, finMod$residuals, colour = BounceRate,  data = training, xlab = "Fitted", ylab = "Residuals")
```


###Plot fitted versus residuals 
```{r, echo=FALSE, fig.height=5, fig.width=6}
qplot(.fitted, .resid, data = finMod) +
  geom_hline(yintercept = 0) +
  geom_smooth(se = FALSE)
```


###Predict training and testing datasets
```{r comment=NA, echo=FALSE}
pred <- predict(modFit, training)
pred1 <- predict(modFit, testing)

head(pred);head(pred1)
```


###Plot predictive models
```{r, echo=FALSE, fig.height=5, fig.width=8}
g1 <- ggplot(training, aes(BounceRate, pred)) + geom_point(size = 2, colour = "blue") + geom_smooth(method="lm", se= FALSE, col="red",size = 1.5) +
  labs(x = "Visits" ) + labs( y = "Bounce Rate") + ggtitle("Training Set / RMSE = 8.92")


g2 <- ggplot(testing, aes(BounceRate, pred1)) + geom_point(size = 2, colour = "blue") + geom_smooth(method="lm", se= FALSE, col="red",size = 1.5) +
  labs(x = "Visits" ) + labs( y = "Bounce Rate") + ggtitle("Testing Set / RMSE = 8.84")

grid.arrange(g1, g2, ncol = 2)
```

