---
title: "Predicting with regression"
output: 
  html_document: 
    highlight: espresso
    theme: cerulean
---
***

[Multiple linear regression](https://en.wikipedia.org/wiki/General_linear_model) is a generalization of linear regression by considering more than one independent variable, and a specific case of general linear models formed by restricting the number of dependent variables to one.


```{r, echo=FALSE, message=FALSE}

require(ggplot2)
require(GGally)
require(reshape2)
social <- read.csv("~/GitHub/Machine_Learning/social.csv", stringsAsFactors = F)
```

<br>

###Fit model, view summary and generate prediction
```{r comment=NA, echo=FALSE}
fit.lm <- lm(social$Visits ~ social$NewVisits + social$BounceRate, data = social)

summary(fit.lm);
coef(fit.lm);
summary(fit.lm)$r.squared;
confint(fit.lm);
pred <- predict(fit.lm,social);
head(pred)
```


```{r, echo=FALSE}
social2 <- social[,c("Visits","NewVisits","BounceRate","PageViews","Session")]

social3 = melt(social2, id.vars='Visits')
```

<br>

###Plot correaltion on each variable
```{r, echo=FALSE,fig.height=5,fig.width=8}
ggplot(social3) +
 geom_jitter(aes(value,Visits, colour=variable),) + geom_smooth(aes(value,Visits, colour=variable), method=lm, se=FALSE) +
  facet_wrap(~variable, scales="free_x") +
  labs(x = "Percentage cover (%)", y = "Number of individuals (N)")
```

<br>

###Diagnostic plots for Linear Models (LM)
```{r, echo=FALSE,fig.height=5,fig.width=8,message=FALSE}
my_fn <- function(data, mapping, ...){
  p <- ggplot(data = data, mapping = mapping) + 
    geom_point() + 
    geom_smooth(method=loess, fill="red", color="red", ...) +
    geom_smooth(method=lm, fill="blue", color="blue", ...)
  p
}

p = ggpairs(social,columns = 3:6, lower = list(continuous = my_fn),diag = list(continuous = wrap("barDiag", colour = "blue")))
p
```

<br>

###Plot fitted vs residuals color by social
```{r, echo=FALSE,fig.height=5,fig.width=8}
qplot(fit.lm$fitted,fit.lm$residuals, colour = Social, data = social, xlab = "Fitted", ylab = "Residuals")
```

<br>

###Plot multivariable regression
```{r, echo=FALSE,fig.height=5,fig.width=8}
p <- ggplot(social, aes(Visits, pred)) + geom_point(size = 2, colour = "blue")
p + geom_smooth(method="lm", se= TRUE, col="red",size = 1.5) +
  labs(x = "Visits" ) +
  labs(y = expression(frac(Model,Response))) +
  labs(title = "Visits vs Bounce Rate + Page Views Relationship")  
```
