---
title: "Tidy Data in R"
output: 
  html_document: 
    highlight: espresso
    theme: cerulean
---
***

## The Structure of Tidy Data

1.Each variable in a dataset should be in one column

2.Each observation of that variable should be in a different row

3.There should be only one table for each kind of variable
***

###Let's view an example

Example1 - Transforming this dataset in order to have each variable in a column and each observation in a row. 

This dataset was created in R to demonstrate a common type of untidy
data

<br>

**Before**

```{r comment=NA, echo=FALSE, message=FALSE}
library(dplyr)
library(tidyr)
n=20
product_revenue <- data.frame(
  Product_ID = sample(paste0("XDS", 1:20)),
  Country = rep(c('CAN','USA'), each = 10),
  Costco.01 = sample(1000:10000,n,replace=TRUE),
  Walmart.01 = sample(1000:10000,n,replace=TRUE),
  Costco.02 = sample(1000:10000,n,replace=TRUE),
  Walmart.02 = sample(1000:10000,n,replace=TRUE)
  )

head(product_revenue)
```

<br>

**After**
```{r comment=NA, echo=FALSE}
product_revenue <- product_revenue %>%
  gather(key, Sales, -Product_ID, -Country) %>%
  separate(key,into = c("Store", "Transit" )) %>%
  arrange(Product_ID, Country, Store ) %>%
  spread(Store, Sales)

head(product_revenue)

```

<br>

Example2 - Transforming this dataset by splitting a single column into four real variables: LastName - FirstName - Title - PhoneNumber

This dataset was created in Excel to demonstrate another common problem with messy data: Many variables are stored in one column

<br>

**Before**
```{r comment=NA, echo=FALSE}
customer <- read.csv("~/GitHub/Cleaning_Data/Customers.csv", stringsAsFactors = F)

head(customer)
```

<br>

**After**
```{r comment=NA, echo=FALSE}
customer <- customer %>%
  separate(Contact.Person, c("LastName","FirstName","Title","PhoneNumber"),sep =  "/")  

customer$PhoneNumber <- gsub(x=customer$PhoneNumber,pattern= "[[:punct:]]", replacement = ' ')  

```

<br>

```{r showtable, results='asis', echo=FALSE}
library(xtable)
xt <-xtable(head(customer))
print(xt, type = "html")


```

