---
title: "Simple linear regression"
output: 
  html_document: 
    highlight: espresso
    theme: cerulean
---
***
####[Simple linear regression](https://en.wikipedia.org/wiki/Simple_linear_regression) is the least squares estimator of a linear regression model with a single explanatory variable. In other words, simple linear regression fits a straight line through the set of n points in such a way that makes the sum of squared residuals of the model (that is, vertical distances between the points of the data set and the fitted line) as small as possible.


```{r, echo=FALSE, message=FALSE}

require(ggplot2)
require(ggfortify)
require(GGally)
forecast <- read.csv("~/GitHub/Regression_Models/forecast.csv",stringsAsFactors = T)
```

<br>

###Fit model, view summary and generate prediction
```{r comment=NA, echo=FALSE}
lm.fit=lm(Sold.units ~ Cost.per.unit ,data = forecast)

summary(lm.fit);
coef(lm.fit);
summary(lm.fit)$r.squared;
confint(lm.fit);
pred <- predict(lm.fit,forecast);
head(pred)
```

<br>

###View correlation between variables
```{r comment=NA , echo=FALSE,fig.height=5,fig.width=8, message=FALSE}
lowerFn <- function(data, mapping, method = "lm", ...) {
  p <- ggplot(data = data, mapping = mapping) +
    geom_point(colour = "blue") +
    geom_smooth(method = method, color = "red", ...)
  p
}

ggpairs(
  forecast[, 3:4], lower = list(continuous = wrap(lowerFn, method = "lm")),
  diag = list(continuous = wrap("barDiag", colour = "blue")),
  upper = list(continuous = wrap("cor", size = 10))
)
```

<br>

###Diagnostic plots for Linear Models (LM)
```{r, echo=FALSE,fig.height=5,fig.width=8,message=FALSE}
autoplot(lm.fit, which = 1:6, label.size = 3, data = forecast,
         colour = 'Color')
```

<br>

###Plot fitted vs residuals 
```{r, echo=FALSE,fig.height=5,fig.width=8}
qplot(.fitted, .resid, data = lm.fit) +
  geom_hline(yintercept = 0) +
  geom_smooth(se = FALSE)
```

<br>

###Plot predicion linear regression model
```{r, echo=FALSE,fig.height=5,fig.width=8}
g <- ggplot(forecast, aes(Cost.per.unit, Sold.units)) + geom_point(size = 3)

g + geom_smooth(method="lm", se=FALSE, col="steelblue",size = 2) +
  labs(x = "Cost/Unit" ) +
  labs(y = expression(frac(Sold.units,Cost.per.unit))) +
  labs(title = "Sold Units - Cost/Unit Relationship")  +
  annotate("text", x = 75, y = 13000, label = "y = 102.04x - 191.64
           r.squared 0.93")
```
